\copyrightVincent

\begin{frame}[fragile]%{What are packages?}
    \begin{columns}
        \begin{column}{\textwidth}
            {\large\textbf{What are packages?}}

            \LaTeX-code written by other people. They can add new commands, change how your
            document looks, or improve existing functionalities.
            
            Example:
            package `xcolor' provides the command \mintinline{tex}{\textcolor{red}{some text}}.

            \bigskip

            {\large Syntax: \mintinline{tex}{\usepackage[aa=6cm,bb,cc=red]{xxx}}}

            \smallskip
            Imports package `xxx'. The optional argument is a list of instructions.
        \end{column}
    \end{columns}
\end{frame}

\begin{frame}[fragile]%{Most essential packages}
    \begin{columns}
        \begin{column}{\textwidth}
            {\large\textbf{Most essential packages}}

            \begin{enumerate}[label=\textbullet]
                \item \textbf{Math packages: amsmath, amssymb}
                
                Defines \mintinline{tex}{\begin{pmatrix}}-environment, which is a
                matrix with parentheses.

                \medskip
                \item \textbf{Layout packages: geometry}
                
                \begin{minted}{tex}
                    \usepackage[a4paper,margin=2.54cm]{geometry}
                \end{minted}

                % This reduces the oversized default margins, and ensures we are using A4-paper

                \medskip
                \item \textbf{Other}: \textbf{graphicx}, \textbf{babel}
                
                Graphicx fixes and improves use of images,
                Babel translates default terms, e.g. `Inhoudsopgave' instead of `Contents'.
            \end{enumerate}
            
            \bigskip
            \centering

            {\small Available packages are managed by CTAN. On their website you find package manuals.}

            \begin{center}
                \textit{Exercises and examples from this presentation will not work if you forget required
                    packages. For a good starting point, see \textnormal{\url{https://vkuhlmann.com/latex/example}}.%
                }
            \end{center}

            % Example:\\
            % \mintinline{tex}{\section{Introduction}}

            % \begin{enumerate}[label=\arabic*)]
            %     \item \textbf{Backslash:} we are starting a command
            %     \item \textbf{Command name:} `section', place a header in the
            %     document. Takes 1 argument.
            %     \item \textbf{Argument 1:} the name of the section
            % \end{enumerate}
        \end{column}
    \end{columns}
\end{frame}